\documentclass[]{article}

% Packages
\usepackage[nottoc,notlof,notlot]{tocbibind} 
\usepackage[margin=1in]{geometry}
\usepackage{changepage}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{titletoc}
\usepackage [english]{babel}
\usepackage [autostyle, english = american]{csquotes}
\usepackage{lmodern}
\usepackage{sectsty}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{Architectural Requirements}
\fancyhead[C]{}
\fancyhead[R]{Last revised: 10 August 2017}
\renewcommand{\headrulewidth}{0.4pt}
\fancyfoot[L]{Code 9}
\fancyfoot[C]{}
\fancyfoot[R]{Page \thepage}
\renewcommand{\footrulewidth}{0.4pt}

\sectionfont{\fontfamily{lmss}\selectfont}
\subsectionfont{\fontfamily{lmss}\selectfont}
% TOC levels
\setcounter{tocdepth}{4}
\setcounter{secnumdepth}{4}

% Title Page
\begin{document}\thispagestyle{empty}\fontfamily{lmss}\selectfont	
	\tableofcontents
	\clearpage
	\section{Functional Requirements}
		\subsection{FR1: Employee Functions}
			\begin{itemize}
				\item \textbf{FR1.1}: An employee will be able to log in to their account on the system
				\item \textbf{FR1.2}: An employee will be able to create their own profile with their        respective skills and previous work experience
				\item \textbf{FR1.3}: An employees will receive a notification when they are assigned to a    newly created project 
				
				\item \textbf{FR1.4}: An Employee must be able to to view their currently assigned           project and view their past completed projects that where assigned        to them on their profile. 
				
				\item \textbf{FR1.5}: An employee will be able to add personal or other events to the        calendar their calender, that do not clash with any existing               projects they are currently assigned to. If a newly created event        does clash, an error will be displayed.  
				
				\item \textbf{FR1.6}: When an employee clicks on a project in the calendar, it will show     all the project details and a map of the clients location should be       displayed as well as directions to the client.
				
				\item \textbf{FR1.7}: An employees will not be able to remove a project that is assigned     to them from their calender.
				
				\item \textbf{FR1.8}: Employees should confirm whether they have attended training or not, this will be conformed with trainer.
			\end{itemize}
	
	\subsection{FR2: Manager functions}
	\begin{itemize}
		\item \textbf{FR2.1}: A manager will be able to log in and create a project.
		
		\item \textbf{FR2.2}: A manager will be able to assign system recommended employees to a      newly created projects
		
		\item \textbf{FR2.3}: A manager will be able change employees if the manager is unhappy with     the recommendation by the system, pending director approval.
		
		\item \textbf{FR2.4}: A manager will be allowed to remove a project from the system, pending director approval
		
		\item \textbf{FR2.5}: A project manager will be able to view all projects that they are managing
	\end{itemize}
	

	\subsection{FR3: System Functions}
	\begin{itemize}
		\item \textbf{FR3.1}: The system will assign employees to a project based
		on their skill level and past project experience. 
		
		\item \textbf{FR3.2}: The system will find all the employees that have the required skills     for the job and give it to the manager as a recommendation.
		
		\item \textbf{FR3.3}: The system will only select employees if they are not already           assigned to a project.
		
		\item \textbf{FR3.4}: Employee data with skills and past work experience
		will be entered on the system and updated after each project. 
		
		\item \textbf{FR3.5}: System will reassign another employee, pending 
		approval, if an employee takes leave during the project.
		
		\item \textbf{FR3.6}: Every employee that is assigned to a project will get
		the full project duration and details on their calendar. 
		
		\item \textbf{FR3.7}: The system should be able to provide the location of and direction      to the client to all employees assigned to the respective project
		
		\item \textbf{FR3.8}:The system will preload all employees training dates
		at the beginning of the year. 
		
		
		\item \textbf{FR3.9}: The system will preload all employees training dates at the beginning of the year.
	\end{itemize}
	
	\end{document}