\documentclass{article}

\begin{document}

\section{Functional Requirements}
	\begin{itemize}
		\item \textbf{FR1}: A manager will be able to login and create a project.
		
		\item \textbf{FR2}: The system will find all the employees that have the required skills for the job and give it to the manager as a recomendation.
		
		\item \textbf{FR3}: The system will find all the employees that have the required skills for the job and give it to the manager as a recomendation.
		
		\item \textbf{FR4}: The system will only select employees if they are not already assigned to a project.
		
		\item \textbf{FR5}: Manager will be able change employees if the manager is unhappy with the recomendation by the system, pending director approval.
		
		\item \textbf{FR6}: Employees will recieve a notification when they are assigned to a project.
		
		\item \textbf{FR7}: Every employee that is assigned to a project will get the full project duration and details on their calendar.
		
		\item \textbf{FR8}: System will reassign another employee, pending approval, if an employee takes leave during the project.
		
		\item \textbf{FR9}: Employee data with skills and past work experience will be entered on the system and updated after each project.
		
		\item \textbf{FR10}: The system will assign employees to a project based on their skill level and past project experience. 
		
		\item \textbf{FR11}: Employees will not be able to remove the project from their calendar.
		
		\item \textbf{FR12}: The system will preload all employees training dates at the beginning of the year.
		
		\item \textbf{FR13}: Employees should confirm wheather they have attended training or not, this will be conformed with trainer.
		
	\end{itemize}

\end{document}
